Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-02 ms.tex
Added equation for central occupation

@@

To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}. In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal15}. In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for comprehensive documentation on all aspects of the {\tt Halotools} framework.

@@

>>>>

\newcommand{\mvir}{M_{\rm vir}}
\newcommand{\ncen}{N_{\rm cen}}
\newcommand{\nsat}{N_{\rm sat}}

@@

To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}. In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal15}. In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for further details.

@@

In standard HOD models, there are two types of galaxies: centrals and satellites. The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively. $P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo is supposed to have only either zero or one central galaxy. So the occupation statistics of central galaxies is specified by its first moment, which we model as

\begin{equation}
\label{eq:ncen}
\langle N_{\mathrm{cen}} \rangle_{M} =
        \frac{1}{2}\left( 1 +
        \mathrm{erf}\left( \frac{\log_{10}M -
        \log_{10}M_{min}}{\sigma_{\log_{10}M}} \right) \right)
\end{equation}
